How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		&\textbf{Number of}&\\
		&\textbf{projects}&\textbf{Percentage}\\
		\hline
		Retrieved & 250,166 & \\
		Analyzed & 247,798 & \\
		Non-empty (used for statistics) & \textbf{233,491} & \\
		\hline
		Procedures & 17,979 & 7.70\%\\
		Recursive procedures &  1,052 & 0.45\%\\
		Variables & 73,577 & 31.51\% \\
		Lists & 9,358 & 4.01\% \\
		Conditional statements & 92,959 & 39.81\% \\
		User input blocks& 131,314 & 56.24\% \\
		Loop statements & 180,210 & 77.18\% \\
		\texttt{repeat until <condition>} statements & 31,739 & 13.59\% \\
		\texttt{broadcast} - \texttt{receive} statements & 69,039 & 29.57\%\\
		Cloned scripts across sprites & 59,634 & 25.54\% \\
		Cloned scripts within sprites & 23,671 & 10.14\%\\
		Cloned procedures & 4,945 & 2.12\%\\
		Cloned functionality blocks across sprites & 60,554 & 25.93\%\\
		Exact clones across sprites & 27,574 & 11.81\%\\
		Exact clones within sprites & 2,043 & 0.87\%\\
		Dead code & 56,890	& 24.36\%\\
		Large scripts & 69,521 & 29.77\%\\
		Large sprites & 31,954 & 13.68\%\\		
		\hline
	\end{tabular}
	\caption{Characteristics in the projects in the dataset}
	\label{tbl-characteristics}
\end{table*}

>>>>

\begin{table}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		&\textbf{\# projects}&\textbf{\%}\\
		\hline
		Retrieved & 250,166 & \\
		Analyzed & 247,798 & \\
		Non-empty (used for statistics) & \textbf{233,491} & \\
		\hline
		Procedures & 17,979 & 7.70\%\\
		Recursive procedures &  1,052 & 0.45\%\\
		Variables & 73,577 & 31.51\% \\
		Lists & 9,358 & 4.01\% \\
		Conditional statements & 92,959 & 39.81\% \\
		User input blocks& 131,314 & 56.24\% \\
		Loop statements & 180,210 & 77.18\% \\
		\texttt{repeat until <condition>} & 31,739 & 13.59\% \\
		\texttt{broadcast} - \texttt{receive} & 69,039 & 29.57\%\\
		Cloned scripts across sprites & 59,634 & 25.54\% \\
		Cloned scripts within sprites & 23,671 & 10.14\%\\
		Cloned procedures & 4,945 & 2.12\%\\
		Cloned blocks across sprites & 60,554 & 25.93\%\\
		Exact clones across sprites & 27,574 & 11.81\%\\
		Exact clones within sprites & 2,043 & 0.87\%\\
		Dead code & 56,890	& 24.36\%\\
		Large scripts & 69,521 & 29.77\%\\
		Large sprites & 31,954 & 13.68\%\\		
		\hline
	\end{tabular}
	\caption{Characteristics in the projects in the dataset}
	\label{tbl-characteristics}
\end{table}
